---
title: "Lab 7 - multiple linear regression"
author: "Cristina Robinson"
date: "11/8/2021"
output: html_document
---

```{r setup, include= TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
# attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Intro to ggpairs

Use GGally::ggpairs() function to create a pairs plot.

```{r}
ggpairs(penguins)
```
```{r}
penguins %>% # start with data
  select(species, bill_length_mm:body_mass_g) %>% #all columns in data from one to the other
  ggpairs(aes(color = species)) # intersection of variables on x and y with graphs in middle 
                                # customize with species color

ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) + # closer look at bill length and body mass 
  geom_point(aes(color = species)) + # differentiates with species 
  geom_smooth(method = "lm") # adds linear regression line # Simpson's paradox without grouping with species
```
## Multiple linear regression - penguins

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass).

```{r}
penguins_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Return just the coefficients:
penguins_lm
```

How would you interpret this coefficient for flipper_length_mm?

  We would expect, on average, a 51.54 g increase in penguin body mass for each 1 mm increase in flipper length, if everything else    is constant. 

Use `summary()` function to get more information:
```{r}
summary(penguins_lm)
```

Bill depth (pr = 0.0892) is the only variable where we would not accept the null hypothesis. 

What does 0.7596 adjusted R-squared value mean for this scenario?

  This means that 76% variance is explained by this model.
  
### Use `broom` functions tidy and glance

Use broom::tidy to get the coefficient summary in a data frame. 
Use broom::glance to get the model summary in a data frame. 

```{r}
penguin_lm_tidy <- tidy(penguins_lm)
penguin_lm_tidy
```

Try using in-line code to refer to (print) the bill depth coefficient. 

`r penguin_lm_tidy$estimate[3]`.

```{r}
penguin_lm_glance <- glance(penguins_lm)

penguin_lm_glance
```
## Try another model

We have thought really hard, done a literature review, consulted with experts, deeply explored our data and decided that the three most critical variables to include in this model (with body mass at the outcome variable) are: 

- flipper length
- species
- sex

Task: create a multiple linear regression model using those 3 predictor variables

Then take a look at the model outputs and interpret the coefficients with a neighbor 

  What I did below:

```{r}
penguins_task<- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

penguins_task
```

  What Allison did:

```{r}
penguin_lm_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

penguin_lm_2
```

How would we interpret these coefficients? 
  
  (Reference level for species is Adelie, and for sex is female)
  
  If everything else is constant, then on average, we expect a Gentoo penguin to weigh 836.26 grams more than an Adelie         penguin. 
  
  If everything else is constant, then on average, we expect Chinstrap penguins will be smaller than Adelies by 87.63 grams. 
  
  If everything else is constant, then on average, we expect a male penguin to weigh 530.38 grams more than a female penguin. 
  
### Use broom::augment() to see predicted values

```{r}
augment(penguin_lm_2) # for predicted values of data frame 
```

## Use plot() to look at model diagnostics 

```{r}
plot(penguin_lm_2) # check residuals for normal distribution (1 and 3 should be similar)
```

- Conceptual understanding and expertise allows me to responsibly determine that penguin species, sex, and flipper length are responsible predictor variables (make sure you're thinking hard about variables and different variable combinations)
- Diagnostic plots all check out for normality of residuals, homoscedasticity, and no worrisome outliers (<< last one is not an assumption)

Make output tables
can use kable extra or stargazer
```{r}

```


Using stargazer:

```{r, results = "asis"}
stargazer(penguin_lm_2, type = "html")
```

